### 2018-05-16 Sections/economics_of_the_quantum_internet.tex
Minor coins

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function QuantCoin($\hat{U}_\text{comp}$, blockchain, data, reward):
\begin{enumerate}
	\item Alice possesses the raw $data$ she would like computed upon, as well as a $reward$ to pay for its processing (in arbitrary units). This could be in the form of QuantCoins, dollars, or other assets of monetary value.
	\item Bob possesses the universal quantum computer, which implements $\hat{U}_\text{comp}$.
	\item Alice encrypts her data using either homomorphic encryption, or a blind quantum computing protocol,
		\begin{align}
			encryptedInput = homoEncrypt(data)
		\end{align}
	\item Alice commits the $encryptedInput$ to the public $blockchain$,
	\begin{align}
	blockchain.commit(encryptedInput)	
	\end{align}
	\item Alice pays Bob the $reward$ to process her data,
	\begin{align}
		give(reward, Alice\to Bob)
	\end{align}
	\item Bob processes the $encryptedInput$ on his quantum computer,
	\begin{align}
		encryptedOutput = \hat{U}_\text{comp}(encryptedInput)
	\end{align}
	\item Bob commits the encrypted output data to the public blockchain,
	\begin{align}
	blockchain.commit(encryptedOutput)	
	\end{align}
	\item Alice and Bob execute a verification protocol,
	\begin{align}
	proof = verify(encryptedOutput)	
	\end{align}
	\item The $proof$ is committed to the $blockchain$ (as is every step of the proof if it is an interactive one),
	\begin{align}
		blockchain.commit(proof)
	\end{align}
	\item The $blockchain$ network inspects that the verification is valid.
	\item If it is valid, the $blockchain$ cryptographically hashes the data and proof, encapsulating it into a QuantCoin\texttrademark\,token, which is given to Bob,
	\begin{align}
		&token = SHA256(encryptedInput + encryptedOutput + proof)\nonumber\\
		&Bob.receive(token)
	\end{align}
\end{enumerate}}}}
\caption{A rough high-level outline for how a quantum computation-backed cryptocurrency might be implemented\footnote{Note this is merely a highly simplified toy model in which all computations are of equal value, which will typically not be the case in the real world. A consumer-ready implementation would have to handle these and other additional details. However, we expect these finer details oughtn't alter the overall flavour of the protocol as described.}. We have abstracted away the underlying Blockchain protocol, interfacing with it using of a high-level API, so as to abstract away the underlying Blockchain technology, which is liable to change substantially in the coming years -- it might even be a natively quantum Blockchain. We similarly call upon verification subroutines using a high-level implementation-dependent API.} \label{alg:quant_coin}
\end{table}

@@

What relationships characterise the value of QuantCoins? First, in a perfectly efficient market we have,
\begin{align}\label{eq:value_quantcoins}
	&(\text{Dollar value of a QuantCoin\texttrademark\,}) \nonumber\\
	&+ (\text{Dollar value of reward paid by Alice for execution}) \nonumber\\
	&= (\text{Dollar value of cost of execution for Bob}).
\end{align}

@@

\comment{More here}

>>>>

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function QuantCoin($\hat{U}_\text{comp}$, blockchain, data, reward):
\begin{enumerate}
	\item Alice possesses the raw input $data$, as well as a $reward$ to pay for its processing (in arbitrary units).
	\item Bob possesses the universal quantum computer, which implements $\hat{U}_\text{comp}$.
	\item Alice encrypts her data using either homomorphic encryption, or a blind quantum computing protocol,
		\begin{align}
			encryptedInput = homoEncrypt(data)
		\end{align}
	\item Alice commits the $encryptedInput$ to the public $blockchain$,
	\begin{align}
	blockchain.commit(encryptedInput)	
	\end{align}
	\item Alice pays Bob the $reward$ to process her data,
	\begin{align}
		give(reward, Alice\to Bob)
	\end{align}
	\item Bob processes the $encryptedInput$ on his quantum computer,
	\begin{align}
		encryptedOutput = \hat{U}_\text{comp}(encryptedInput)
	\end{align}
	\item Bob commits the encrypted output data to the public blockchain,
	\begin{align}
	blockchain.commit(encryptedOutput)	
	\end{align}
	\item Alice and Bob execute a verification protocol,
	\begin{align}
	proof = verify(encryptedOutput)	
	\end{align}
	\item The $proof$ is committed to the $blockchain$ (as is every step of the proof if it is an interactive one),
	\begin{align}
		blockchain.commit(proof)
	\end{align}
	\item The $blockchain$ network inspects that the verification is valid.
	\item If valid, the $blockchain$ cryptographically hashes the data and proof, encapsulating it into a QuantCoin\texttrademark\,token, which is given to Bob,
	\begin{align}
		&token = SHA256(encryptedInput + encryptedOutput + proof)\nonumber\\
		&Bob.receive(token)
	\end{align}
\end{enumerate}}}}
\caption{A rough high-level outline for how a quantum computation-backed cryptocurrency might be implemented\footnote{This is merely a highly simplified toy model in which all computations are of equal value. A consumer-ready implementation would have to handle these and other additional implementation details. However, we expect these finer details ought not alter the overall flavour of the protocol.}. We have abstracted away the underlying Blockchain protocol, interfacing with it using a high-level API. We do this since Blockchain technology is highly liable to change substantially in the coming years -- it might even be a natively quantum Blockchain. We similarly call upon verification subroutines using a high-level implementation-dependent API.} \label{alg:quant_coin}
\end{table}

@@

What relationships characterise the value of QuantCoins? First, in a perfectly efficient market (Sec.~\ref{post:market_eff}) we have,
\begin{align}\label{eq:value_quantcoins}
	&(\text{Dollar value of a QuantCoin\texttrademark\,}) \nonumber\\
	&+ (\text{Dollar value of reward paid by Alice for execution}) \nonumber\\
	&= (\text{Dollar value of cost of execution for Bob}).
\end{align}

@@

Note that with exception to the scenario where Alice buys into QuantCoins\texttrademark\, using dollar currency, the entire protocol is self-enforcing via Blockchain transactions. Bob doesn't get paid his newly earned and freshly printed QuantCoin\texttrademark\, until the verification of the computation has completed and the proof committed to the Blockchain. He therefore cannot get paid until he has executed the computation he promised to, and proven to the network that he actually did.

The main security risk is that of Bob taking Alice's dollars and running, upon receiving the upfront reward in dollars, which necessarily don't reside on the Blockchain since they are not crypto-assets. This could be addressed by introducing trusted third-party escrow agents into the protocol.

However, if the upfront payment were being made in pre-existing QuantCoins\texttrademark\,, the Blockchain might be programmed to not release the reward until completion of the final verification stage of the protocol -- effectively an escrow programmed directly into the Blockchain for execution.

As described above, the cryptocurrency is effectively backed by the spot market in computation -- we exchange currency for the execution of computations \textit{immediately}. However, one might also envisage more complex cryptocurrencies being backed by the futures market in the licensing of quantum compute-time. Intuitively, one would expect such a form of cryptocurrency to be sounder than the one backed by the spot market. This is because our spot market-derived coins, once mined are not guaranteed to be convertible to anything of value, including computations. Recall that the execution of the computation takes place immediately when the coin is created. On the other hand, a QuantCoin\texttrademark\, backed by a guarantee to access quantum compute-time at a designated point in the future necessarily has value, so long as the demand for compute-time does, and maintains value until the contract matures and converts into compute-time at which point it becomes worthless.
